---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ssdtests

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/ssdtests/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/ssdtests/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ssdtests is to hold the slow and unstable tests for the
[ssdtools](https://github.com/bcgov/ssdtools) package.
It has no user-facing functionality of its own.

A test belongs here rather than in ssdtools when it cannot run reliably or
quickly as part of ssdtools' own CRAN-facing suite: exact parametric bootstrap
confidence-limit snapshots that are not reproducible across platforms, slow
tests such as fitting every curated dataset to every distribution, and
numerically unstable fits.
ssdtools keeps the fast, portable, structural assertions for the same code
paths.

The tests are organised by subject in `tests/testthat/` (one
`test-<subject>.R` file per distribution or function), and
`scripts/ssdtools-coverage.R` reports the ssdtools coverage the suite produces.
See `vignette("ssdtests")` for an overview and `CONTRIBUTING.md` for the
conventions.

## Installation

You can install the development version of ssdtests from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
pak::pak("bcgov/ssdtests")
```

```{r, results = "asis", echo = FALSE}
cat(ssdtests::ssdtests_licensing_md())
```

