---
title: "Rescaling Effect on Distribution Fitting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rescaling Effect on Distribution Fitting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup}
library(ssdtests)
```

## Background

By default `ssdtools` does not rescale data when fitting distributions so that the parameter estimates can be used directly to estimate the HCx values.
However, if `rescale = TRUE` in the `ssd_fit_dists()` or `ssd_fit_burrlioz()` functions then the data is rescaled by dividing by the geometric mean of the minimum and maximum positive finite values.
To examine the extent to which model fitting success is improved by fitting the `length(ssdtools::ssd_dists_all())` distributions currently implemented in `ssdtools` to the `r length(unique(envirotox::envirotox_acute$Chemical))` acute datasets in `envirotox` with and without rescaling.

##

```{r}
library(ssdtools)
library(envirotox)

dists <- ssdtools::ssd_dists_all()

data <- envirotox::envirotox_acute |>
#  dplyr::slice(1:12) |>
  dplyr::nest_by(Chemical) |>
  dplyr::mutate(ssd_fit_unscale = list(ssdtools::ssd_fit_dists(data, dists = dists, silent = TRUE)),
                ssd_fit_rescale = list(ssdtools::ssd_fit_dists(data, dists = dists, rescale = TRUE, silent = TRUE))) |>
  dplyr::mutate(dists_unscale = list(names(ssd_fit_unscale)),
                dists_rescale = list(names(ssd_fit_rescale))) |>
  dplyr::select(!c(ssd_fit_unscale, ssd_fit_rescale))

unscaled <- data |>
  dplyr::select(Chemical, dists_unscale) |>
  tidyr::unnest(dists_unscale) |>
  dplyr::ungroup() |>
  dplyr::count(dists_unscale) |>
  dplyr::mutate(n = n / nrow(data) * 100) |>
  dplyr::select(dist = dists_unscale, unscaled = n)

rescaled <- data |>
  dplyr::select(Chemical, dists_rescale) |>
  tidyr::unnest(dists_rescale) |>
  dplyr::ungroup() |>
  dplyr::count(dists_rescale) |>
  dplyr::mutate(n = n / nrow(data) * 100) |>
  dplyr::select(dist = dists_rescale, rescaled = n)

results <- unscaled |>
  dplyr::inner_join(rescaled, by = "dist")
```

```{r, echo = FALSE}
knitr::kable(results, digits = 1)
```



To examine
